Statically Typed String Sanitation Inside a Python

### 2014-08-19 sanitation-psp14/sanitation-psp14-short.tex
small changes to sec2

\section{Regular String Types, Minimally}\label{calculus}

In this section, we define a minimal typed lambda calculus with regular string types called $\lambda_{RS}$. The syntax of $\lambda_{RS}$ is specified in Figure \ref{fig:glambdas}, its static semantics in Figure \ref{fig:slambdas} and its evaluation semantics in Figure \ref{fig:dlambdas}. %This will serve as the source language for our translation to a calculus with only standard strings and regular expressions, defined in Section~\ref{sec:tr}.

An outline for this section follows:
\begin{itemize}
\item Section \ref{sec:rs} describes these rules. We also give proof outlines of  type safety and correctness theorems.
\item Section \ref{sec:p} describes a simple target language, $\lambdap$, with a minimal regular expression library. In Section \ref{atlang}, we will take Python to be such a language.
\item Section \ref{sec:tr} describes the translation from $\lambdas$ to $\lambdap$ and ensures the correcness result for \ref{sec:rs} is preserved under translation. 
\end{itemize}

\subsection{The Language of Regular Strings}\label{sec:rs}
There are two type constructors in $\lambdas$, $\rightarrow$ and $\textsf{stringin}$. Arrow types classify functions, which are introduced via lambda abstraction, $\lambda x.e$, and can be applied, written $e(e)$, in the usual way \cite{pfpl}. Regular string types are of the form $\stringin{r}$, where $r$ is a regular expression. Values of such regular string types take the form $\strin{s}$, where $s$ is a string (i.e. $s \in \Sigma^\star$, defined in the usual way). The rule \textsc{S-T-Stringin-I} statically guarantees that $s \in \lang{r}$.\footnote{For convenience, a single sheet containing Figures \ref{fig:glambdas}-\ref{fig:tr} is available at http://nfulton.org/strings/printout.pdf.}.
 %The remaining operations on terms of type $\stringin{r}$ preserve this property. %The remaining operators operate on regular strings.

>>>>

\section{Regular String Types, Minimally}\label{calculus}
\noindent
%This will serve as the source language for our translation to a calculus with only standard strings and regular expressions, defined in Section~\ref{sec:tr}. 
This section is organized as follows:
\begin{itemize}
\item Section \ref{sec:rs} describes $\lambda_{RS}$. We also give proof outlines of  type safety and correctness theorems.
\item Section \ref{sec:p} describes a simple target language, $\lambdap$, with a minimal regular expression library. In Section \ref{atlang}, we will take Python to be such a language.
\item Section \ref{sec:tr} describes the translation from $\lambdas$ to $\lambdap$ and ensures the correcness result for \ref{sec:rs} is preserved under translation. 
\end{itemize}

\subsection{The Language of Regular Strings}\label{sec:rs}
In this section, we define a minimal typed lambda calculus with regular string types called $\lambda_{RS}$. The syntax of $\lambda_{RS}$ is specified in Figure \ref{fig:glambdas}, its static semantics in Figure \ref{fig:slambdas} and its evaluation semantics in Figure \ref{fig:dlambdas}.\footnote{For convenience, a single sheet containing Figures \ref{fig:glambdas}-\ref{fig:tr} is available at http://nfulton.org/strings/printout.pdf.}

There are two type constructors in $\lambdas$, $\rightarrow$ and $\textsf{stringin}$. Arrow types classify functions, which are introduced via lambda abstraction, $\lambda x.e$, and can be applied, written $e(e)$, in the usual way \cite{pfpl}. Regular string types are of the form $\stringin{r}$, where $r$ is a regular expression. Values of such regular string types take the form $\strin{s}$, where $s$ is a string (i.e. $s \in \Sigma^\star$, defined in the usual way). The rule \textsc{S-T-Stringin-I} statically guarantees that $s \in \lang{r}$.
 %The remaining operations on terms of type $\stringin{r}$ preserve this property. %The remaining operators operate on regular strings.
